Preventing runtime errors of Redis at compile time

### 2015-11-18 paper.tex
6. Making Redis Polymorphic

@@

With functions on dictionaries, now we could annotate the effects of a command
in types. \mintinline{text}{DEL} removes a key from the current database,
regardless of its type.

@@

In the type of \mintinline{haskell}{del}, the type varabile
\mintinline{haskell}{s} would be a \mintinline{haskell}{Symbol} that is decided
 by the argument of type \mintinline{haskell}{Proxy s}.
To use \mintinline{haskell}{del}, we would have to apply it with a clunky
 term-level proxy like this:

@@

So far, the datatypes we are dealing with, are all of those built-in Redis data
structures, such as \emph{strings}, \emph{lists (of strings)},
\emph{sets (of strings)}, etc.
But in the real world, these raw strings are hardly useful, people would
usually serialize their data into strings before storing them, and deserialize
them back when in need.

Instead of letting users writing these boilerplates, we will be doing these
serializations/deserializations for them. With the help from
\mintinline{text}{cereal}, a binary serialization library.

\mintinline{text}{cereal} comes with these two functions:
\begin{minted}[xleftmargin=1em]{haskell}
encode :: Serialize a
       => a -> ByteString Source

@@

\footnotetext{The methods of \mintinline{haskell}{Serialize} will have default
generic implementations for all datatypes with some language extenstions
enabled}

\section{Imposing constraints}

@@

In Edis we implemented five of them.

\section{Conclusions and Related Work}

>>>>

To execute a \mintinline{haskell}{Edis} program, simply apply it to
 \mintinline{haskell}{unEdis} to get an ordinary
 \mintinline{haskell}{Hedis} program, with type informations erased.

@@

Now we could annotate the effects of a command in types.
\mintinline{text}{DEL} removes a key from the current database,
regardless of its type.

@@

In the type of \mintinline{haskell}{del}, the type varabile
\mintinline{haskell}{s} would be a \mintinline{haskell}{Symbol} that is decided
 by the argument of type \mintinline{haskell}{Proxy s}.
To use \mintinline{haskell}{del}, we would have to apply it with a clumsy
 term-level proxy like this:

@@

Redis supports many different datatypes, these datatypes as can be viewed as
\emph{containers} of strings. For example, lists (of strings),
sets (of strings), and strings themselves.

\section{Denoting containers}
Most Redis commands only work with a certain type of these containers. To
annotate what container a key is associated with, we introduce these container
types.

\begin{minted}[xleftmargin=1em]{haskell}
data Strings
data Lists
data Sets
...
\end{minted}

\mintinline{text}{SET} stores a string, regardless the datatype the key was
 associated with. Now we could implement \mintinline{text}{SET} like this:

\begin{minted}[xleftmargin=1em,fontsize=\footnotesize]{haskell}
set :: KnownSymbol s
    => Proxy s
    -> ByteString       -- data to store
    -> Edis xs (Set xs s Strings) (Either Reply Status)
set key val = Edis $ Hedis.set (symbolVal key) val
\end{minted}

After \mintinline{text}{SET}, the key will be associated with
\mintinline{haskell}{Strings} in the dictionary, indicating that it's a string.
%
% So far, the datatypes we are dealing with, are all of those built-in Redis data
% structures, such as \emph{strings}, \emph{lists (of strings)},
% \emph{sets (of strings)}, etc.

\subsection{Automatic data serialization}
But in the real world, raw binary strings are hardly useful, people would
usually serialize their data into strings before storing them, and deserialize
them back when in need.

Instead of letting users writing these boilerplates, we will be doing these
serializations/deserializations for them. With the help from
\mintinline{text}{cereal}, a binary serialization library.
\mintinline{text}{cereal} comes with these two functions:

\begin{minted}[xleftmargin=1em]{haskell}
encode :: Serialize a
       => a -> ByteString Source

@@

\subsection{Extending container types}
We rename container types and extend it with an extra type arguement,
to indicate what kind of data it's holding.

\begin{minted}[xleftmargin=1em]{haskell}
data StringOf x
data ListOf x
data SetOf x
...
\end{minted}

\mintinline{haskell}{set} reimplemented with extended container types:

\begin{minted}[xleftmargin=1em,fontsize=\footnotesize]{haskell}
set :: (KnownSymbol s, Serialize x)
    => Proxy s
    -> x       -- can be anything, as long as it's serializable
    -> Edis xs (Set xs s (StringOf x)) (Either Reply Status)
set key val = Edis $ Hedis.set (symbolVal key) (encode val)
\end{minted}

For example, if we execute \mintinline{haskell}{set (Proxy :: Proxy "A") True},
a new entry \mintinline{text}{'}\mintinline{haskell}{("A", StringOf Bool)} will
be inserted to the dictionary.

\footnotetext{The methods of \mintinline{haskell}{Serialize} will have default
generic implementations for all datatypes with some language extenstions
enabled, no sweat!}

@@

\section{Discussions}
\section{Conclusions and Related Work}
